
Need to include Held jobs in listing?

Incorportate Travis-CI

Top task: Python bindings: 

\href{https://htcondor.readthedocs.io/en/latest/apis/python-bindings/}{htcondor python bindings}


Automatic generation and usage of container – dependent quantities such as generator lists, configuration files

How is prority defined?

Automatic generation and usuage of experiment – dependent quantities such as background merging file list 


Background merging mechanism


Support multiple containers


Add more control over job flow, output sturcture

Set up Contintious integration



If genOutput is changed to “dvcs.dat” from “dvcsgen1.dat", everything is fine
In the new web_interface I didn’t even include all those generators for this reason. Also, soon we should have the scard object to remove those maps in the fs.py that have the hardcoded names.



) Using online repositoris:
	2.1) Create documentation to describe how to set up online repositories
	2.2) Is there a way to store things the other computer has acress to bypass the internet, maybe on volitle? It can be a pain to upload to remote online repositories. Could we upload to 	github?
Move connect_to_db to utils/utils
Add sqlite option to utils/jsonify_logfile.py



1) Is there a way to get information about what version of gemc / what other versions of the software are in the CVMFS image (which is distributed to all systems, Im guessing?)
	1.1) see what gcards are avaliable?
	1.2) Add way to specifiy specific gcard within docker containe




How will we log the number of events / the number of jobs if the user supplies the gcards / LUND files?
use log output files to monitor job submissions




5.) Work on fixing -w issue -- should not have to use, also gcards should be downloaded on node



2.)
Set up a dynamic list of gcards acceptable 
have list returned to user on what gcards are valid, can assume clas12.gcard & a description of what gcard is / does / has in it


Regarding the gcards, I think it's ok to have them in a file for now. We can wait a few container releases to see if what's in the file matches the container content or it has to be different. 
The command to retrieve the list from the container is straightforward:

singularity exec --home ${PWD}:/srv --pwd /srv --bind /cvmfs --contain --ipc --pid /cvmfs/singularity.opensciencegrid.org/jeffersonlab/clas12simulations:production ls /jlab/work/ | grep gcard

